Xolotl: An Intuitive and Approachable Neuron \& Network Simulator in MATLAB

### 2018-07-11 paper/paper.tex
ready to make network figure (again)

\begin{figure}[!htb]
	\centering
	\includegraphics[width=1.0\linewidth]{gfx/figure_mechanism}
	\caption{Modeling intracellular mechanisms. (box A) A single-compartment neuron model with 8 channel types. With these parameters, this model neuron is a tonic spiker. Since there is no mechanism for changing intracellular Calcium in this model, the Calcium level stays constant (top panel). (box B)  An intracellular buffering of Calcium and the effect of Calcium influx through voltage gated Calcium channels (VGCCs) is modeled using a simple differential equation. Code snippet shows how this mechanism can be added to the neuron model. The cell now bursts periodically, with synchronized oscillations in intracellular Calcium. (box C) Schematic of Calcium-dependent integral control homeostasis (cite O'Leary et al.). In this feedback system, the rates of mRNA synthesis depend on the Calcium level in the cell, which depends on the membrane voltage, which in turn depends on the conductance density of all channel types, which, through translation, is a function of the mRNA abundance. These integral controllers are implemented as \texttt{mechanism} objects, and can be added to conductances. On integrating the model, intracellular calcium levels rise and approach the target (red dashed line). This is accompanied by an increase in the conductance densities of all channels being controlled by this homeostatic mechanism. The voltage behavior of the cell changes from silence to bursting with truncated spikes to regular bursting.}
	\label{fig:figuremechanism}
\end{figure}

>>>>

\begin{figure}[!htb]
	\centering
	\includegraphics[width=1.0\linewidth]{gfx/figure_mechanism}
	\caption{Modeling intracellular mechanisms. (A) A single-compartment neuron model with 8 channel types. Since there is no mechanism for changing intracellular Calcium in this model, the Calcium level stays constant (B), and the cell tonically spikes (C). Intracellular Calcium buffering and influx through voltage gated Calcium channels (VGCCs) can be modeled using a simple differential equation (D). Code snippet shows how this mechanism can be added to the neuron model (E). The cell now bursts periodically, with synchronized oscillations in intracellular Calcium (F-G). (H) Schematic of Calcium-dependent integral control homeostasis (cite O'Leary et al.). In this feedback system, the rates of mRNA synthesis depend on the Calcium level in the cell, which depends on the membrane voltage, which in turn depends on the conductance density of all channel types, which, through translation, is a function of the mRNA abundance. (I) The code snippet shows how these integral controllers are implemented as \texttt{mechanism} objects, and can be added to conductances. (J) On integrating the model, intracellular calcium levels rise and approach the target (red dashed line). This is accompanied by an increase in the conductance densities of all channels being controlled by this homeostatic mechanism (K). The voltage behavior of the cell changes from silence to bursting with truncated spikes to regular bursting.}
	\label{fig:figuremechanism}
\end{figure}
